---
title: "EDA Week 1 Assignment"
output: html_notebook
---

##Assignment Criteria
Was a valid GitHub URL containing a git repository submitted?

Does the GitHub repository contain at least one commit beyond the original fork?

Please examine the plot files in the GitHub repository. Do the plot files appear to be of the correct graphics file format?

Does each plot appear correct?

Does each set of R code appear to create the reference plot?

##Data Definition
Date: Date in format dd/mm/yyyy

Time: time in format hh:mm:ss

Global_active_power: household global minute-averaged active power (in kilowatt)

Global_reactive_power: household global minute-averaged reactive power (in kilowatt)

Voltage: minute-averaged voltage (in volt)

Global_intensity: household global minute-averaged current intensity (in ampere)

Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered).

Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.

Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner.
    
## Prepare the Data
The dataset has 2,075,259 rows and 9 columns. First calculate a rough estimate of how much memory the dataset will require in memory before reading into R. Make sure your computer has enough memory (most modern computers should be fine).  We will only be using data from the dates 2007-02-01 and 2007-02-02. 
    
````{r}
library(readr)
library(dplyr)
library(datasets)

hhdataFile <- "./household_power_consumption.txt"
hhdata <- read.table(hhdataFile, header=TRUE, sep=";", stringsAsFactors=FALSE, dec=".")
plotdata <- hhdata[hhdata$Date %in% c("1/2/2007","2/2/2007") , ]
datetime <- strptime(paste(plotdata$Date, plotdata$Time, sep=" "), "%d/%m/%Y %H:%M:%S")
globalActivePower <- as.numeric(subSetData$Global_active_power)
subMeter1 <- as.numeric(plotdata$Sub_metering_1)
subMeter2 <- as.numeric(plotdata$Sub_metering_2)
subMeter3 <- as.numeric(plotdata$Sub_metering_3)
globalReactivePower <- as.numeric(plotdata$Global_reactive_power)
voltage <- as.numeric(plotdata$Voltage)

````
## Make the Plots
Our overall goal here is simply to examine how household energy usage varies over a 2-day period in February, 2007. Your task is to reconstruct the following plots below, all of which were constructed using the base plotting system.

First you will need to fork and clone the following GitHub repository: https://github.com/rdpeng/ExData_Plotting1

For each plot you should

Construct the plot and save it to a PNG file with a width of 480 pixels and a height of 480 pixels.

Name each of the plot files as plot1.png, plot2.png, etc.

Create a separate R code file (plot1.R, plot2.R, etc.) that constructs the corresponding plot, i.e. code in plot1.R constructs the plot1.png plot. Your code file should include code for reading the data so that the plot can be fully reproduced. You must also include the code that creates the PNG file.

Add the PNG file and R code file to the top-level folder of your git repository (no need for separate sub-folders)

The follow code blocks represent each of the plot outputs.  

### Plot 1
````{r}
# Plot 1: Simple histogram 
plot1 <- hist(data2$Global_active_power, main = "Global Active Power", xlab = "Global Active Power (kilowatts)", col = "red")
dev.copy(png, file = "Plot1.png")
dev.off()

````

### Plot 2
````{r}
png("plot2.png", width = 480, height = 480)
plot(datetime, globalActivePower, type = "l", main = "Global Active Power: 1-2 Feb 2007", xlab = "", ylab = "Global Active Power")
dev.off()

````

### Plot 3
````{r}
png("plot3.png", width = 480, height = 480)
plot(datetime, subMeter1, type = "l", xlab = "", ylab = "Engery Sub Meter Reading")
lines(datetime, subMeter2, type = "l", col = "red")
lines(datetime, subMeter3, type = "l", col = "blue")
legend("topright", c("Sub Meter 1", "Sub Meter 2", "Sub Meter 3"), lty = 1,   col = c("black", "red", "blue"))
dev.off()

````

### Plot 4
````{r}
png("plot4.png", width = 480, height = 480)
par(mfrow = c(2,2))

#plot 4.1: top left, same as plot 1
plot(datetime, globalActivePower, type = "l", main = "Global Active Power: 1-2 Feb 2007", xlab = "", ylab = "Global Active Power")

#plot 4.2: top right, with Voltage
plot(datetime, voltage, type = "l", xlab = "datetime", ylab = "Voltage")

#plot 4.3: bottom left, same as plot 3
plot(datetime, subMeter1, type = "l", xlab = "", ylab = "Engery Sub Meter Reading")
lines(datetime, subMeter2, type = "l", col = "red")
lines(datetime, subMeter3, type = "l", col = "blue")
legend("topright", c("Sub Meter 1", "Sub Meter 2", "Sub Meter 3"), lty = 1,   col = c("black", "red", "blue"))

#plot 4.4: bottom right, with Global Reactive Power
plot(datetime, globalReactivePower, type = "l", xlab = "datetime", ylab = "Global Reactive Power")

dev.off()

````